### 2020-05-31 report/sections/server/codegen/workflow.tex
Report: commented notes for chapter 3

>>>>

We introduce the high-level system architecture of \fancyname{SessionTS}
in \cref{fig:workflow}.

\begin{itemize}

\item We integrate with the \fancyname{Scribble} toolchain to
specify the protocol, validate its well-formedness and 
formalise and validate the well-formedness of the communication protocol.

The communication protocol is specified using \fancyname{Scribble},

\end{itemize}

\cref{fig:cmdline} outlines the information required at the entry
point of \fancyname{SessionTS}:

\begin{itemize}

\item The protocol and role name are required to

\end{itemize}

The developer provides the following information at the 
command line entry point:
\textbf{(1)} the protocol to generate,
\textbf{(2)} the role to generate for, 
\textbf{(3)} the code generation target.
We adopt different code generation strategies for back-end 
(\cref{chap:node}) and front-end (\cref{chap:react}) implementations.

, and conditionally
\textbf{(4)} the server role.
